
```{r}
setwd("D:/Files/Imp Files/Great Learning/All Courses/9-Marketing and Retail Analytics")
getwd()
```

```{r}
mktBasket=read.table("MBA.csv",sep=",",header=TRUE)
print(mktBasket)
mktBasket$Quantity = as.numeric(mktBasket$Quantity)
mktBasket$Rate = as.numeric(mktBasket$Rate)
mktBasket$Tax = as.numeric(mktBasket$Tax)
mktBasket$Discount = as.numeric(mktBasket$Discount)
mktBasket$Total = as.numeric(mktBasket$Total)
print(mktBasket)

```

The 'split' function takes the first parameter and groups them with respect to the invoice numbers

```{r}


mktBasket.Agg=split(mktBasket$Item.Desc,mktBasket$Bill.Number)
head(mktBasket.Agg)
```

We see that in the invoice number 100009 the person has only bought one kind of goods. We need to remove the duplicates.




```{r}
mktBasket.Agg2=list()
for(i in 1:length(mktBasket.Agg)){
  mktBasket.Agg2[[i]]=unique(mktBasket.Agg[[i]])
}
head(mktBasket.Agg2)
```



```{r}

library(arules)# 'arules' has a specific data structure called Transactions
Txns=as(mktBasket.Agg2,"transactions")
summary(Txns)
inspect(Txns[10])#here we are looking at the 10th transactions
```


```{r}
freq=itemFrequency(Txns)#gives us the frequency of each items
freq=freq[order(-freq)]#gives the frequencies in descending order
freq["1 AXE TWIST"]#gives the frequency of Bread
barplot(freq[1:20])#first 20 items barplot
itemFrequencyPlot(Txns,support=.1)
itemFrequencyPlot(Txns,topN=10)

```

Let us build the association rules.

```{r}
arules=apriori(data=Txns)
inspect(sort(arules,by="lift"))
```

The 'apriori' function has a lot of default rules. Let us see what happens if we override them.

```{r}
arules2=apriori(data=Txns,
                  parameter=list(support=0.001,confidence=0.005,maxlen=2)
                )
inspect(sort(arules2,by='lift'))
```

Now let us plot arules2. We are plotting 'confidence' vs 'support' with 'lift' as a colour gradient.

```{r}
library(RColorBrewer)#we are using this library to plot the colour as a gradient rather than a single colour
library(arulesViz)
plot(arules2,control=list(col=brewer.pal(11,"Spectral")),jitter=0)#the plot function now works on the basis of the arulesViz package
#ideally, here we are looking for something on the top right corner with a deep red
```

Since the above plot is giving us 719 rules, we might not get a proper inference from this. Thus, we are looking at the top 20 rules(sorted by support) to give us a better clarity.

```{r}
subrules2=head(sort(arules2,by="lift"),10)
inspect(subrules2)
plot(subrules2,method="graph")
```

```{r}
rules_df=as(arules2,"data.frame")#here we are converting arules2 in to a data frame
#Rule: {A}=>{B}
#Probability(A)-LHS Support
rules_df$LHSSupport=rules_df$support/rules_df$confidence#gives us the probability of A on the LHS
#Probability(B)-RHS Support
rules_df$RHSSupport=rules_df$confidence/rules_df$lift#gives us the probability of B on the RHS
print(rules_df)#here we can finally use the print command rather than inspect as it has been converted in to a data frame
write.table(rules_df,file="MBA_output.csv",sep=",",append=FALSE,row.names = FALSE)
```


